### 2016-01-06 p2/intro.tex
Fix typo

In terms of the usual classification of synchronizers (\cite{TSR, PV, SSH}),
our approach to reconciliation is therefore operation-based as we investigate sets of commands,
while the update detection algorithm makes the full synchronizer 
similar to state-based synchronizers 
as its starting point is the states of the replicase themselves.
Moreover, our ordering algorithms only depend on the properties of commands 
such as commutativity or idempotence,
and therefore they can be classified as semantic schedulers.
This is in opposition to syntactic scheduling, which uses 
the origin and original temporal order of updates, 
and which may give rise to otherwise resolvable conflicts (\cite{SSH}).
Ordering plays a central role in other operation-based synchronizers.
We refer to a survey by Saito and Shapiro of so-called optimistic replication algorithms (\cite{SSH});
or, in particular,
to IceCube, where multiple orders are tested to find an acceptable one (\cite{KRSD}, see also \cite{MPV}),
or Bayou, where reconciling updates happens by redoing them in a globally determined order \cite{TTPDSH}.

>>>>

In terms of the usual classification of synchronizers (\cite{TSR, PV, SSH}),
our approach to reconciliation is therefore operation-based as we investigate sets of commands,
while the update detection algorithm makes the full synchronizer 
similar to state-based synchronizers 
as its starting point is the states of the replicas themselves.
Moreover, our ordering algorithms only depend on the properties of commands 
such as commutativity or idempotence,
and therefore they can be classified as semantic schedulers.
This is in opposition to syntactic scheduling, which uses 
the origin and original temporal order of updates, 
and which may give rise to otherwise resolvable conflicts (\cite{SSH}).
Ordering plays a central role in other operation-based synchronizers.
We refer to a survey by Saito and Shapiro of so-called optimistic replication algorithms (\cite{SSH});
or, in particular,
to IceCube, where multiple orders are tested to find an acceptable one (\cite{KRSD}, see also \cite{MPV}),
or Bayou, where reconciling updates happens by redoing them in a globally determined order \cite{TTPDSH}.
